Visualizing demographic evolution using geographically inconsistent census data

### 2019-08-08 paper/method.tex
one last review

Each aspect is represented by a stacked bar plot, where the width of each
rectangle corresponds to the average percentage of that variable over the
considered period. In this case, about half of the people in Chicago in the
considered period are married, and the percentage that are Widowers or Divorced
is roughly similar. About half of the population work in Administrative jobs, a
third never completed high-school, approximately half have gross family income
below 50,000USD per year. The vast majority identify as white. Placing the mouse
over one of the bars will open a small panel with the temporal evolution of that
specific variable, and clicking on the chevron on the right side expands the
corresponding aspect, showing details of the temporal evolution of each variable
and also the corresponding IQRs for the whole city.

>>>>

%TODO THIS IS WRONG!
Each aspect is represented by a stacked bar plot, where the width of each
rectangle corresponds to the average percentage of that variable over the
considered period. In this case, about half of the people in this region, in the
considered period, are married, and the percentage that are Widowers or Divorced
is roughly similar. About half of the population work in Administrative jobs, a
third never completed high-school, approximately half have gross family income
below 50,000USD per year. The vast majority identify as white. Placing the mouse
over one of the bars will open a small panel with the temporal evolution of that
specific variable, and clicking on the chevron on the right side expands the
corresponding aspect, showing details of the temporal evolution of each variable
and also the corresponding IQRs for the whole city.
